Making Sequential Programs Deterministic

### 2019-04-06 related.tex
related todo

\todo{I don't see how the first two (especially the first) citations in the
  next paragraph are related to our work.  Make the connection explicit, or
  remove them.}

The problem of inconsistencies between specifications and implementations
is quite prevalent.~\cite{Jin:2012:UDR:2254064.2254075} looks at the effect of inefficient code sequences on the performance of software.
Its findings suggest that incorrect understanding of performance specifications of APIs is a very common root cause for
performance bugs. ~\cite{Rui:2013:180377} analyzes the APIs related to security such as authorization and authentication.
These APIs which come as a part of the SDKs provided by online providers are used by application developers to 
build secure apps. The paper discovers that the security guarantees provided by these SDKs are violated due to
the implicit assumptions made by the APIs that the users are unaware of. In \cite{Xiao:2014:NMC:2591062.2591177},
the authors
study the effect of nondeterminism in MapReduce programs with a specific focus on nondeterminism caused by
non-commutative reducers. While they found bugs that violated correctness due to this bug pattern,
the authors reported that several of these were harmless as they relied on an implicit assumption on data
which ensured correctness.

>>>>

%\todo{I don't see how the first two (especially the first) citations in the
%  next paragraph are related to our work.  Make the connection explicit, or
%  remove them.}

The problem of inconsistencies between specifications and implementations
is quite prevalent. Other researchers have explored ways of reducing the gap between implicit
specifications in APIs and the assumptions made by their clients in a variety of problem domains.
The findings in~\cite{Jin:2012:UDR:2254064.2254075} suggest that incorrect understanding of performance specifications of 
APIs is a very common root cause for
performance bugs. ~\cite{Rui:2013:180377} analyzes the APIs related to security such as authorization and authentication.
These APIs which come as a part of the SDKs provided by online providers are used by application developers to 
build secure apps. The paper discovers that the security guarantees provided by these SDKs are violated due to
the implicit assumptions made by the APIs that the users are unaware of. In \cite{Xiao:2014:NMC:2591062.2591177},
the authors
study the effect of nondeterminism in MapReduce programs with a specific focus on nondeterminism caused by
non-commutative reducers. While they found bugs that violated correctness due to this bug pattern,
the authors reported that several of these were harmless as they relied on an implicit assumption on data
which ensured correctness.
